---
title: "B205683_Assessment"
author: "B205683"
date: "2022/6/21"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```


[Link to my git repository] (https://github.com/B205683/B205683_assessment.git)

# Data dictionary for test data
```{r pressure, echo=FALSE}
#loading the packages and data needed for this script.
library(NHSRdatasets)
library(dataMeta)
library (tidyverse)
library(here)

#Load the LOS_model data.
data(LOS_model)

# Have a look at the LOS_model data
data(LOS_model)
LOS<-LOS_model
class(LOS)
#The tbl_df class is a subclass of data.frame. 
# Look at the summary of teh LOS_model data
summary(LOS_model)
#printing
LOS

#The LOS_model tibble consists of 300 rows of data and 5 columns with different classes. 
```
## **Variable descriptions**
```{r variable_description}
variable_description <- c("an integer value fictional patient ID number.",
"A factor,stands for 1of 10 fictional hospital trusts, e.g. “Trust1.","an integer, representing the age of fictional patient in years.","‘Length of Stay,’ an integer representing the number of days a patient was in hospital.","an integer flag of the status of patients (0 = survived, 1= died in hospital).") 

print(variable_description)
```
## **Variable types**
```{r glimpse2}
glimpse(LOS) 
```
We have one quantitative values (measured values) variables and four fixed values (allowable values or codes) variables.
```{r variable_type} 
variable_type <- c(0, 1, 0, 1, 0)
print(variable_type)
```
## linker 
```{r build_linker}
linker<-build_linker(LOS, variable_description, variable_type)
print(linker)
```
```{r dictionary}
dictionary <- build_dict(my.data = LOS, linker = linker)
glimpse(dictionary) 
```

```{r w,message = FALSE, warning = FALSE}
glimpse(dictionary)
```
## **Append data dictionary to the CollectedData**

#### **Create main_string for attributes**
```{r main_string}
main_string <- "This data describes an artificially generated hospital data. Fictional patients at 10 fictional hospitals, with LOS, Age and Death status data from the *NHSRdatasets*."
main_string
```
```{r complete_dataset}
complete_LOSData <- incorporate_attr(my.data = LOS, data.dictionary = dictionary,
main_string = main_string)
#Change the author name
attributes(complete_LOSData)$author[1]<-"B205687"
complete_LOSData
attributes(complete_LOSData)
```



## Calculate how many NAs there are in each variable
```{r NAs}
LOS %>% 
  map(is.na) %>%
map(sum)
#The data is complete.

LOS <- rowid_to_column(LOS, "index")
```

## Including Plots
# Look at the distribution of Length of Stay (LOS)
```{r distribution}

ggplot(LOS_model, aes(x=LOS)) +
  geom_histogram(alpha=0.5, col=1, fill=13, bins=20)+
  ggtitle("Distribution of Length of Stay")

```
